Paper Plots V1

### 2025-02-08 Rmd/paper_plots/paper_plots_1.2.Rmd
run some updated scenarios

1. Time series of new ISS vs old. Accompanied by number of hauls, nominal sample size, and possibly RSS boxplots. RSS boxplots may help justify focusing in on 20 sample size meidan for later plots to get an apples to apples, granular test of impact of sample size and expansion complexity.

2. ISS full, ISS without expansion, ISS without sampling strata, ISS without either.

3. 3x3 grid: sample size 10, 20, 30 fixed X expansion none, haul only, haul+month. With sampling strata.

3.supp.1: same as above but without sampling strata. 
3.supp.2: same as above but without bootstrapping trip. 
3.supp.3: same as above but without either.

## Plot 1.1
```{r}
out_1.1 = readRDS(file = "C:/Users/bstacy2/OneDrive - UW/UW Postdoc/GitHub Repos/baseISS_data/outputs/paper_output/paper_scenario_1.1_ISS_100iters_output_2024-11-25.RDS")

out_1.2 = readRDS(file = "C:/Users/bstacy2/OneDrive - UW/UW Postdoc/GitHub Repos/baseISS_data/outputs/paper_output/paper_scenario_1.2_ISS_1iters_output_2025-01-10.RDS")

out_1.3 = readRDS(file = "C:/Users/bstacy2/OneDrive - UW/UW Postdoc/GitHub Repos/baseISS_data/outputs/paper_output/paper_scenario_1.3_ISS_100iters_output_2025-01-22.RDS")

@@

out_2.1 = readRDS(file = "C:/Users/bstacy2/OneDrive - UW/UW Postdoc/GitHub Repos/baseISS_data/outputs/paper_output/paper_scenario_2.2_ISS_500iters_output_2025-01-28.RDS")

out_3.1 = readRDS(file = "C:/Users/bstacy2/OneDrive - UW/UW Postdoc/GitHub Repos/baseISS_data/outputs/paper_output/paper_scenario_3.1_ISS_100iters_output_2024-11-26.RDS")

out_4.1 = readRDS(file = "C:/Users/bstacy2/OneDrive - UW/UW Postdoc/GitHub Repos/baseISS_data/outputs/paper_output/paper_scenario_4.2_ISS_500iters_output_2025-01-28.RDS")

out_5.1 = readRDS(file = "C:/Users/bstacy2/OneDrive - UW/UW Postdoc/GitHub Repos/baseISS_data/outputs/paper_output/paper_scenario_5.2_ISS_500iters_output_2025-01-27.RDS")

out_6.1 = readRDS(file = "C:/Users/bstacy2/OneDrive - UW/UW Postdoc/GitHub Repos/baseISS_data/outputs/paper_output/paper_scenario_6.1_ISS_100iters_output_2024-11-26.RDS")
out_7.1 = readRDS(file = "C:/Users/bstacy2/OneDrive - UW/UW Postdoc/GitHub Repos/baseISS_data/outputs/paper_output/paper_scenario_7.1_ISS_100iters_output_2024-11-26.RDS")
out_8.1 = readRDS(file = "C:/Users/bstacy2/OneDrive - UW/UW Postdoc/GitHub Repos/baseISS_data/outputs/paper_output/paper_scenario_8.1_ISS_100iters_output_2024-11-26.RDS")
out_9.1 = readRDS(file = "C:/Users/bstacy2/OneDrive - UW/UW Postdoc/GitHub Repos/baseISS_data/outputs/paper_output/paper_scenario_9.2_ISS_500iters_output_2025-01-27.RDS")
out_10.1 = readRDS(file = "C:/Users/bstacy2/OneDrive - UW/UW Postdoc/GitHub Repos/baseISS_data/outputs/paper_output/paper_scenario_10.1_ISS_100iters_output_2024-12-04.RDS")
out_11.1 = readRDS(file = "C:/Users/bstacy2/OneDrive - UW/UW Postdoc/GitHub Repos/baseISS_data/outputs/paper_output/paper_scenario_11.1_ISS_100iters_output_2024-12-04.RDS")
out_12.1 = readRDS(file = "C:/Users/bstacy2/OneDrive - UW/UW Postdoc/GitHub Repos/baseISS_data/outputs/paper_output/paper_scenario_12.1_ISS_100iters_output_2024-12-10.RDS")
out_13.1 = readRDS(file = "C:/Users/bstacy2/OneDrive - UW/UW Postdoc/GitHub Repos/baseISS_data/outputs/paper_output/paper_scenario_13.1_ISS_100iters_output_2024-12-10.RDS")
out_14.1 = readRDS(file = "C:/Users/bstacy2/OneDrive - UW/UW Postdoc/GitHub Repos/baseISS_data/outputs/paper_output/paper_scenario_14.1_ISS_100iters_output_2024-12-10.RDS")
out_15.1 = readRDS(file = "C:/Users/bstacy2/OneDrive - UW/UW Postdoc/GitHub Repos/baseISS_data/outputs/paper_output/paper_scenario_15.1_ISS_100iters_output_2024-12-10.RDS")
out_16.1 = readRDS(file = "C:/Users/bstacy2/OneDrive - UW/UW Postdoc/GitHub Repos/baseISS_data/outputs/paper_output/paper_scenario_16.1_ISS_100iters_output_2024-12-11.RDS")
out_17.1 = readRDS(file = "C:/Users/bstacy2/OneDrive - UW/UW Postdoc/GitHub Repos/baseISS_data/outputs/paper_output/paper_scenario_17.1_ISS_100iters_output_2024-12-11.RDS")

@@

### baseISS with assessment ISS

```{r}
par(mfrow = c(1,1), mar = c(1.5, 3.1, 0, .5), mgp = c(2, .6, 0))
plot(out_1.1$length$iss$YEAR, out_1.1$length$iss$iss, type = "l", ylab = "ISS", xlab = "year", cex.lab = 1.3, ylim = c(0, max(out_1.1$length$iss$iss)*1.1), col = "blue") 
lines(assessment_2023_iss$year, assessment_2023_iss$iss, col = "black")
legend("topleft", lty = c(1,1), col = c("black", "blue"), legend = c("2023 assessment", "baseISS"))

### All together 4 panel

```{r, fig.height=8}
df = data.frame(rss = out_1.1$length$rss$rss, year = as.factor(out_1.1$length$rss$YEAR))

# par(mfrow = c(4,1), mar = c(0,0,0,0), oma = c(2, 4, 2, .5), mgp = c(2, .6, 0))
par(mfrow = c(4,1), mar = c(1.5, 3.1, 0, .5), mgp = c(2, .6, 0))
plot(out_1.1$length$iss$YEAR, out_1.1$length$iss$iss, type = "l", ylab = "ISS", xaxt = "n") 
lines(assessment_2023_iss$year, assessment_2023_iss$iss, col = "blue")
legend("topleft", lty = c(1,1), col = c("black", "blue"), legend = c("2023 assessment", "baseISS"))

plot(out_1.1$length$iss$YEAR, out_1.1$length$iss$nhls, type = "l", ylab = "number of hauls", xlab = "", col = "black", cex.lab = 1.3, xaxt = "n")

plot(out_1.1$length$iss$YEAR, out_1.1$length$iss$nss, type = "l", ylab = "nominal sample size", xlab = "", cex.lab = 1.3, xaxt = "n")

plot(df$year, df$rss, ylim = c(0, 20000), ylab = "RSS", cex.lab = 1.3, xlab = "year")

### All together 3 panel

```{r, fig.height=8}
df = data.frame(rss = out_1.1$length$rss$rss, year = as.factor(out_1.1$length$rss$YEAR))

# par(mfrow = c(4,1), mar = c(0,0,0,0), oma = c(2, 4, 2, .5), mgp = c(2, .6, 0))
# par(mfrow = c(3,1), mar = c(1.5, 3.1, 0, .5), mgp = c(2, .6, 0))
par(mfrow = c(3,1), mar = c(0,3.1,0,0), oma = c(2, 0, 2, .5), mgp = c(2, .6, 0))
plot(out_1.1$length$iss$YEAR, out_1.1$length$iss$iss, type = "l", ylab = "ISS", xaxt = "n", ylim = c(0, 15000)) 
lines(assessment_2023_iss$year, assessment_2023_iss$iss, col = "blue")
lines(out_1.1$length$iss$YEAR, out_1.1$length$iss$nhls, col = "red")
legend("topleft", lty = c(1,1,1), col = c("black", "blue", "red"), legend = c("ISSB", "ISSA", "number of hauls"))

plot(out_1.1$length$iss$YEAR, out_1.1$length$iss$nss, type = "l", ylab = "nominal sample size", xlab = "", cex.lab = 1.3, xaxt = "n")

plot(df$year, df$rss, ylim = c(0, 20000), ylab = "RSS", cex.lab = 1.3)

### * All together 2 panel

@@

### All together TRIPS TOO 4 panel

```{r, fig.height=8}
df = data.frame(rss = out_1.1$length$rss$rss, year = as.factor(out_1.1$length$rss$YEAR))

# par(mfrow = c(4,1), mar = c(0,0,0,0), oma = c(2, 4, 2, .5), mgp = c(2, .6, 0))
par(mfrow = c(4,1), mar = c(1.5, 3.1, 0, .5), mgp = c(2, .6, 0))
plot(out_1.1$length$iss$YEAR, out_1.1$length$iss$iss, type = "l", ylab = "ISS", xaxt = "n") 
lines(assessment_2023_iss$year, assessment_2023_iss$iss, col = "blue")
legend("topleft", lty = c(1,1), col = c("black", "blue"), legend = c("2023 assessment", "baseISS"))

plot(out_1.1$length$iss$YEAR, out_1.1$length$iss$nhls, type = "l", ylab = "number of hauls", xlab = "", col = "black", cex.lab = 1.3, xaxt = "n")

plot(out_1.2$length$iss$YEAR, out_1.2$length$iss$ntps, ylim = c(0, 1000), ylab = "Number of Trips", type = "l", cex.lab = 1.3, xaxt = "n", xlab = "")

plot(out_1.1$length$iss$YEAR, out_1.1$length$iss$nss, type = "l", ylab = "nominal sample size", cex.lab = 1.3, xlab = "year")

### All together TRIPS TOO 3 panel

```{r, fig.height=8}
df = data.frame(rss = out_1.1$length$rss$rss, year = as.factor(out_1.1$length$rss$YEAR))

# par(mfrow = c(4,1), mar = c(0,0,0,0), oma = c(2, 4, 2, .5), mgp = c(2, .6, 0))
# par(mfrow = c(3,1), mar = c(1.5, 3.1, 0, .5), mgp = c(2, .6, 0))
par(mfrow = c(3,1), mar = c(0,3.1,0,0), oma = c(2, 0, 2, .5), mgp = c(2, .6, 0))
plot(out_1.1$length$iss$YEAR, out_1.1$length$iss$iss, type = "l", ylab = "ISS", xaxt = "n", ylim = c(0, 15000)) 
lines(assessment_2023_iss$year, assessment_2023_iss$iss, col = "blue")
lines(out_1.1$length$iss$YEAR, out_1.1$length$iss$nhls, col = "red")
lines(out_1.2$length$iss$YEAR, out_1.2$length$iss$ntps, col = "green")
legend("topleft", lty = c(1,1,1), col = c("black", "blue", "red"), legend = c("ISSB", "ISSA", "number of hauls"))

plot(out_1.1$length$iss$YEAR, out_1.1$length$iss$nss, type = "l", ylab = "nominal sample size", xlab = "", cex.lab = 1.3, xaxt = "n")

plot(df$year, df$rss, ylim = c(0, 20000), ylab = "RSS", cex.lab = 1.3)

### All together TRIPS TOO 4 panel sample rate by HAUL on bottom

```{r, fig.height=8}
df = data.frame(rss = out_1.1$length$rss$rss, year = as.factor(out_1.1$length$rss$YEAR))

# par(mfrow = c(4,1), mar = c(0,0,0,0), oma = c(2, 4, 2, .5), mgp = c(2, .6, 0))
# par(mfrow = c(3,1), mar = c(1.5, 3.1, 0, .5), mgp = c(2, .6, 0))
par(mfrow = c(4,1), mar = c(0,3.1,0,0), oma = c(2, 0, 2, .5), mgp = c(2, .6, 0))
plot(out_1.1$length$iss$YEAR, out_1.1$length$iss$iss, type = "l", ylab = "ISS", xaxt = "n", ylim = c(0, 15000)) 
lines(assessment_2023_iss$year, assessment_2023_iss$iss, col = "blue")
lines(out_1.1$length$iss$YEAR, out_1.1$length$iss$nhls, col = "red")
# lines(out_1.2$length$iss$YEAR, out_1.2$length$iss$ntps, col = "green")
legend("topleft", lty = c(1,1,1), col = c("black", "blue", "red"), legend = c("ISSB", "ISSA", "number of hauls"))

plot(out_1.4$length$iss$YEAR, out_1.4$length$iss$ntps, type = "l", ylab = "number of trips", xlab = "", cex.lab = 1.3, xaxt = "n")
plot(out_1.1$length$iss$YEAR, out_1.1$length$iss$nss, type = "l", ylab = "nominal sample size", xlab = "", cex.lab = 1.3, xaxt = "n")

# plot(df$year, df$rss, ylim = c(0, 20000), ylab = "RSS", cex.lab = 1.3)
out_1.4$length$freq_data_frame %>% 
  tidytable::summarise(samples_per_haul = unique(YAGMH_SFREQ), .by = c(YEAR, HAUL_JOIN)) %>% 
  tidytable::mutate(YEAR = as.factor(YEAR)) -> df.SpH

df.SpH %>% 
  tidytable::summarise(samples_per_haul_median = median(samples_per_haul), .by = c(YEAR)) %>% 
  tidytable::mutate(YEAR = as.numeric(as.character(YEAR))) -> df.SpH.median

# boxplot
# plot(df.SpH$YEAR, df.SpH$samples_per_haul, ylab = "Samples per Haul", cex.lab = 1.3, ylim = c(0, 400))

# median
plot(df.SpH.median$YEAR, df.SpH.median$samples_per_haul_median, type = "l", ylab = "Haul sample rate", cex.lab = 1.3)

@@

### 1999 and 2000 histograms
```{r, fig.height=8, fig.width=9}
# out_1.4$length$og_props %>% 
#   tidytable::filter(YEAR %in% 1999:2000) %>% 
#   tidytable::mutate(YEAR = as.factor(YEAR)) -> props.sub
# 
# ggplot(data = props.sub, aes(x = LENGTH, y = og_FREQ, colour = YEAR)) +
#   geom_line() +
#   geom_area(aes(fill = YEAR, group = YEAR), alpha = 0.5, position = "identity") +
#   theme_classic() +
#   theme(legend.position = c(0.8, 0.8)) +
#   scale_x_continuous(limits = c(25, 110)) +
#   labs(x = "Length", y = "Frequency")

@@

# violin plot
p2 = ggplot(props.sub, aes(x = rss, y = Year, fill = Year)) +
  geom_violin() +
  theme_classic() +
  stat_summary(fun.y = median, geom = "point", color = "black") +
  theme(legend.position = c(0.8, 0.8),
        plot.tag.position = c(0.1, 0.95),
        plot.tag = element_text(size = 14, face = "bold")) +
  labs(x = "RSS", y = "Year", tag = "B")

p1 / p2
```

#### * Histograms

```{r, fig.height=8, fig.width=9}
# 
# 
# ggplot(props.sub, aes(rss, fill = YEAR)) +
#   geom_histogram(binwidth = 500)
# 
# ggplot(props.sub, aes(rss, colour = YEAR)) +
#   geom_histogram(aes(fill = YEAR, group = YEAR), alpha = 0.5)
#

@@

# +
#   scale_x_continuous(limits = c(22, 108)) +
#   labs(x = "Length", y = "Frequency")

@@

### Simulate Multinomials
```{r}

# rmultinom(1, size = 20, prob = out_1.4$length$og_props[YEAR==2003, c(og_FREQ)])[,1] %>% 
#   hist()

multinom_var = function(n, p) n*p*(1-p)

multinom_var(30, c(.3,.35)) %>% sum()
multinom_var(60, c(.3,.35)) %>% sum()

### Plot new number of hauls vs old

```{r, eval=F}

plot(out_1.1$length$iss$YEAR, out_1.1$length$iss$nhls, col = "red")
lines(out_1.4$length$iss$YEAR, out_1.4$length$iss$nhls, col = "blue")

plot(out_1.1$length$iss$YEAR, out_1.1$length$iss$nss, col = "red")
lines(out_1.4$length$iss$YEAR, out_1.4$length$iss$nss, col = "blue")

plot(out_1.2$length$iss$YEAR, out_1.2$length$iss$ntps, col = "red")
lines(out_1.4$length$iss$YEAR, out_1.4$length$iss$ntps, col = "blue")

out_1.2$length$iss$ntps-out_1.4$length$iss$ntps

###

#### Inspect R-squared
Fit models to number of hauls.

```{r}
# baseISS ~ # hauls
fit1 = lm(out_1.1$length$iss$iss ~ out_1.1$length$iss$nhls)
summary(fit1)

# assessment ISS ~ # hauls
fit2 = lm(assessment_2023_iss$iss ~ out_1.1$length$iss$nhls)
summary(fit2)

# baseISS ~ assessment ISS
fit3 = lm(out_1.1$length$iss$iss ~ assessment_2023_iss$iss)
summary(fit3)

## Plot 2.1 
Deconstruct the contributors to baseISS

### All together 1

Subtracting things from baseISS

```{r, fig.height=8}

# par(mfrow = c(4,1), mar = c(0,0,0,0), oma = c(2, 4, 2, .5), mgp = c(2, .6, 0))
par(mfrow = c(5,1), mar = c(1.5, 3.1, 0, .5), mgp = c(2, .6, 0))
plot(out_1.1$length$iss$YEAR, out_1.1$length$iss$iss, type = "l", ylab = "baseISS", xaxt = "n") 
plot(out_2.1$length$iss$YEAR, out_2.1$length$iss$iss, type = "l", ylab = "baseISS - E", xaxt = "n") 
plot(out_3.1$length$iss$YEAR, out_3.1$length$iss$iss, type = "l", ylab = "baseISS - SS", xaxt = "n") 
plot(out_4.1$length$iss$YEAR, out_4.1$length$iss$iss, type = "l", ylab = "baseISS - (E,SS)", xaxt = "n") 
plot(out_5.1$length$iss$YEAR, out_5.1$length$iss$iss, type = "l", ylab = "baseISS - (E,SS,Bs)", cex.lab = 1.3, xlab = "year") 
```

### All together 2

Adding things to baseISS

```{r, fig.height=6}
par(mfrow = c(1,1))

plot(out_5.1$length$iss$YEAR, out_5.1$length$iss$iss, type = "l", ylab = "ISS", cex.lab = 1.3, col = "black")
lines(out_6.1$length$iss$YEAR, out_6.1$length$iss$iss, type = "l", col = "blue") 
lines(out_7.1$length$iss$YEAR, out_7.1$length$iss$iss, type = "l", col = "orange") 
lines(out_8.1$length$iss$YEAR, out_8.1$length$iss$iss, type = "l", col = "green") 
lines(out_1.1$length$iss$YEAR, out_1.1$length$iss$iss, type = "l", col = "red")

legend("topleft", legend = c("-E,SS,Bs", "-SS,Bs", "-Bs", "-SS", "-0"), lty = c(1,1,1,1,1), col = c("black", "blue", "orange", "green", "red"))
```

#### sub range 1
```{r, fig.height=6}
sub_range = out_5.1$length$iss$YEAR %in% 1999:2023

par(mfrow = c(1,1))
plot(out_5.1$length$iss$YEAR[sub_range], out_5.1$length$iss$iss[sub_range], type = "l", ylab = "ISS", cex.lab = 1.3, col = "black", ylim = c(0, 25000))
lines(out_6.1$length$iss$YEAR[sub_range], out_6.1$length$iss$iss[sub_range], type = "l", col = "blue") 
lines(out_7.1$length$iss$YEAR[sub_range], out_7.1$length$iss$iss[sub_range], type = "l", col = "orange") 
lines(out_8.1$length$iss$YEAR[sub_range], out_8.1$length$iss$iss[sub_range], type = "l", col = "green") 
lines(out_1.1$length$iss$YEAR[sub_range], out_1.1$length$iss$iss[sub_range], type = "l", col = "red")

legend("topright", legend = c("boot length", "boot length and expand", "boot length, expand, sampling strata weighting", "boot length, expand, boot trip+haul", "full"), lty = c(1,1,1,1,1), col = c("black", "blue", "orange", "green", "red"))
```

#### * reorder long

@@

```{r, fig.height=5.5}
sub_range = out_5.1$length$iss$YEAR %in% 1977:2023

par(mfrow = c(1,1))
plot(out_5.1$length$iss$YEAR[sub_range], out_5.1$length$iss$iss[sub_range], type = "l", ylab = "ISSB", cex.lab = 1.3, col = "black", ylim = c(0, 25000), xlab = "Year")
lines(out_9.1$length$iss$YEAR[sub_range], out_9.1$length$iss$iss[sub_range], type = "l", col = "blue") 
lines(out_4.1$length$iss$YEAR[sub_range], out_4.1$length$iss$iss[sub_range], type = "l", col = "orange") 
lines(out_2.1$length$iss$YEAR[sub_range], out_2.1$length$iss$iss[sub_range], type = "l", col = "green")
# lines(out_8.1$length$iss$YEAR[sub_range], out_8.1$length$iss$iss[sub_range], type = "l", col = "green") 
lines(out_1.4$length$iss$YEAR[sub_range], out_1.4$length$iss$iss[sub_range], type = "l", col = "red")

legend("topleft", legend = c("boot length", "boot length + boot haul", "boot all", "boot all + sampling strata weighting", "full"), lty = c(1,1,1,1,1), col = c("black", "blue", "orange", "green", "red"), bty = "n")
```

@@

##### * Inspect 2000, 2001 for expansion drop
```{r}
out_1.4$length$freq_data_frame %>% 
  tidytable::filter(YEAR %in% 2000:2001) %>% 
  tidytable::summarise(YAGMH = unique(YAGMH_SNUM), .by = YEAR) %>% 
  tidytable::mutate(YEAR = as.factor(YEAR)) -> temp1

ggplot(data = temp1, aes(x = YAGMH, colour = YEAR)) +
  geom_histogram(aes(fill = YEAR, group = YEAR), alpha = 0.5, position = "identity") +
  theme_classic()

out_1.4$length$freq_data_frame %>% 
  tidytable::filter(YEAR %in% 2000:2001) %>% 
  tidytable::summarise(YAGM = unique(YAGM_SNUM), .by = YEAR) %>% 
  tidytable::mutate(YEAR = as.factor(YEAR)) -> temp2

ggplot(data = temp2, aes(x = YAGM, colour = YEAR)) +
  geom_histogram(aes(fill = YEAR, group = YEAR), alpha = 0.5, position = "identity") +
  theme_classic()

# inspect huge weighted YAGM over 30,000,000
out_1.4$length$freq_data_frame %>% 
  tidytable::filter(YAGM_SNUM>10000000, YEAR%in%2000:2001) %>% 
  tidytable::mutate(Year = as.factor(YEAR)) -> temp3

temp3 %>% 
  ggplot(aes(x = LENGTH, colour = Year)) +
  geom_histogram(aes(fill = Year, group = Year), alpha = 0.5, position = "identity") +
  theme_classic() +
  scale_x_continuous(limits = c(30, 115))

# maybe gear is responsible: check big AGM category to see if many more fish were caught with trawl net in 2000?

# wait, it should be the combined weight right? so which WEIGHT is that from the expansion? Is it saved in the output?

#### reorder short

```{r, fig.height=6}
sub_range = out_5.1$length$iss$YEAR %in% 1999:2023

par(mfrow = c(1,1))
plot(out_5.1$length$iss$YEAR[sub_range], out_5.1$length$iss$iss[sub_range], type = "l", ylab = "ISSB", cex.lab = 1.3, col = "black", ylim = c(0, 25000), xlab = "")
lines(out_9.1$length$iss$YEAR[sub_range], out_9.1$length$iss$iss[sub_range], type = "l", col = "blue") 
lines(out_4.1$length$iss$YEAR[sub_range], out_4.1$length$iss$iss[sub_range], type = "l", col = "orange") 
lines(out_2.1$length$iss$YEAR[sub_range], out_2.1$length$iss$iss[sub_range], type = "l", col = "green")
# lines(out_8.1$length$iss$YEAR[sub_range], out_8.1$length$iss$iss[sub_range], type = "l", col = "green") 
lines(out_1.1$length$iss$YEAR[sub_range], out_1.1$length$iss$iss[sub_range], type = "l", col = "red")

legend("topright", legend = c("boot length", "boot length + boot haul", "boot all", "boot all + sampling strata weighting", "full"), lty = c(1,1,1,1,1), col = c("black", "blue", "orange", "green", "red"))
```

#### reorder short with half trips and half hauls
```{r, fig.height=6}
sub_range = out_5.1$length$iss$YEAR %in% 1998:2023

par(mfrow = c(1,1))
plot(out_5.1$length$iss$YEAR[sub_range], out_5.1$length$iss$iss[sub_range], type = "l", ylab = "ISS", cex.lab = 1.3, col = "black", ylim = c(0, 25000), xlab = "Year")
lines(out_9.1$length$iss$YEAR[sub_range], out_9.1$length$iss$iss[sub_range], type = "l", col = "blue") 
lines(out_4.1$length$iss$YEAR[sub_range], out_4.1$length$iss$iss[sub_range], type = "l", col = "orange") 
lines(out_12.1$length$iss$YEAR[sub_range], out_12.1$length$iss$iss[sub_range], type = "l", col = "purple")
lines(out_13.1$length$iss$YEAR[sub_range], out_13.1$length$iss$iss[sub_range], type = "l", col = "brown")
lines(out_2.1$length$iss$YEAR[sub_range], out_2.1$length$iss$iss[sub_range], type = "l", col = "green")
lines(out_1.1$length$iss$YEAR[sub_range], out_1.1$length$iss$iss[sub_range], type = "l", col = "red")

legend("topright", legend = c("boot length", "boot length, haul", "boot all", "boot all, half trips", "boot all, half hauls", "boot all, sampling strata weighting", "full"), lty = c(1,1,1,1,1,1,1), col = c("black", "blue", "orange","purple", "brown", "green", "red"))
```

#### reorder short 2
```{r, fig.height=6}
sub_range = out_5.1$length$iss$YEAR %in% 1998:2023

par(mfrow = c(1,1))
plot(out_10.1$length$iss$YEAR[sub_range], out_10.1$length$iss$iss[sub_range], type = "l", ylab = "ISS", cex.lab = 1.3, col = "black", ylim = c(0, 25000), xlab = "Year")
lines(out_11.1$length$iss$YEAR[sub_range], out_11.1$length$iss$iss[sub_range], type = "l", col = "blue")

lines(out_1.1$length$iss$YEAR[sub_range], out_1.1$length$iss$iss[sub_range], type = "l", col = "red")

legend("topright", legend = c("boot.length", "boot.length + boot.haul", "boot.length + boot.haul + boot.trip"), lty = c(1,1,1), col = c("black", "blue", "red"))
```

#### Full, half trip, half haul
```{r, fig.height=6}
sub_range = out_5.1$length$iss$YEAR %in% 1998:2023

par(mfrow = c(1,1))
plot(out_1.1$length$iss$YEAR[sub_range], out_1.1$length$iss$iss[sub_range], type = "l", ylab = "ISS", cex.lab = 1.3, col = "black", ylim = c(0, 25000), xlab = "Year")
lines(out_14.1$length$iss$YEAR[sub_range], out_14.1$length$iss$iss[sub_range], type = "l", col = "blue")

lines(out_15.1$length$iss$YEAR[sub_range], out_15.1$length$iss$iss[sub_range], type = "l", col = "red")

legend("topright", legend = c("Full", "Half Trip", "Half Haul"), lty = c(1,1,1), col = c("black", "blue", "red"))
```

#### Full, 1.5 trip, 1.5 haul
```{r, fig.height=6}
sub_range = out_5.1$length$iss$YEAR %in% 1998:2023

par(mfrow = c(1,1))
plot(out_1.1$length$iss$YEAR[sub_range], out_1.1$length$iss$iss[sub_range], type = "l", ylab = "ISS", cex.lab = 1.3, col = "black", ylim = c(0, 25000), xlab = "Year")
lines(out_16.1$length$iss$YEAR[sub_range], out_16.1$length$iss$iss[sub_range], type = "l", col = "blue")

lines(out_17.1$length$iss$YEAR[sub_range], out_17.1$length$iss$iss[sub_range], type = "l", col = "red")

legend("topright", legend = c("Full", "1.5 Trip", "1.5 Haul"), lty = c(1,1,1), col = c("black", "blue", "red"))
```

## Plot 7x2 Grid Haul and Trip numbers

### Trip Change
```{r}

# out_18.1 = readRDS(file = "C:/Users/bstacy2/OneDrive - UW/UW Postdoc/GitHub Repos/baseISS_data/outputs/paper_output/paper_scenario_18.1_ISS_200_iters_2024-12-12.RDS")
out_18.1 = readRDS(file = "C:/Users/bstacy2/OneDrive - UW/UW Postdoc/GitHub Repos/baseISS_data/outputs/paper_output/paper_scenario_18.2_ISS_200_iters_2025-02-01.RDS")

year = out_18.1$proportion_0.25$type_trip$length$iss$YEAR
proportion_global = c(0.25, 0.50, 0.75, 1.25, 1.50, 1.75, 2.00)
type_global = list("trip", "haul")
type_names_global = c("trip", "haul")

df = tidytable(year = year,
               N_0.25 = out_18.1$proportion_0.25$type_trip$length$iss$iss,
               N_0.50 = out_18.1$proportion_0.5$type_trip$length$iss$iss,
               N_0.75 = out_18.1$proportion_0.75$type_trip$length$iss$iss,
               N_1.00 = out_1.4$length$iss$iss,
               N_1.25 = out_18.1$proportion_1.25$type_trip$length$iss$iss,
               N_1.50 = out_18.1$proportion_1.5$type_trip$length$iss$iss,
               N_1.75 = out_18.1$proportion_1.75$type_trip$length$iss$iss,
               N_2.00 = out_18.1$proportion_2$type_trip$length$iss$iss)

df2 = melt.data.table(df, id.vars = "year", variable.name = "scenario", value.name = "ISS")
df2.trip = df2

ggplot(data = df2, aes(x = year, y = ISS, group = scenario, colour = scenario)) +
  geom_line() +
  labs(x = "Year", y = "ISS") +
  geom_point() +
  ylim(0, 17000) +
  xlim(1998, 2023)

### Boxplots
REMEMBER! these are the full year range, may want to narrow it to recent range.
```{r}
df2 %>% 
  tidytable::mutate(ISS.diff = (df2$ISS[df2$scenario=="N_1.00"]) - ISS,
                    ISS.error = (ISS - df2$ISS[df2$scenario=="N_1.00"])/df2$ISS[df2$scenario=="N_1.00"],
                    type = "trip",
                    .by = scenario) -> df3.1

# plot(df3$scenario, df3$ISS.diff)
plot(df3.1$scenario, df3.1$ISS.error)
abline(h = c(-.1,.1), lty = "dashed")

### Haul Change
```{r}

# out_18.1 = readRDS(file = "C:/Users/bstacy2/OneDrive - UW/UW Postdoc/GitHub Repos/baseISS_data/outputs/paper_output/paper_scenario_18.1_ISS_200_iters_2024-12-12.RDS")
out_18.1 = readRDS(file = "C:/Users/bstacy2/OneDrive - UW/UW Postdoc/GitHub Repos/baseISS_data/outputs/paper_output/paper_scenario_18.2_ISS_200_iters_2025-02-01.RDS")

year = out_18.1$proportion_0.25$type_trip$length$iss$YEAR
proportion_global = c(0.25, 0.50, 0.75, 1.25, 1.50, 1.75, 2.00)
type_global = list("trip", "haul")
type_names_global = c("trip", "haul")

df = tidytable(year = year,
               N_0.25 = out_18.1$proportion_0.25$type_haul$length$iss$iss,
               N_0.50 = out_18.1$proportion_0.5$type_haul$length$iss$iss,
               N_0.75 = out_18.1$proportion_0.75$type_haul$length$iss$iss,
               N_1.00 = out_1.4$length$iss$iss,
               N_1.25 = out_18.1$proportion_1.25$type_haul$length$iss$iss,
               N_1.50 = out_18.1$proportion_1.5$type_haul$length$iss$iss,
               N_1.75 = out_18.1$proportion_1.75$type_haul$length$iss$iss,
               N_2.00 = out_18.1$proportion_2$type_haul$length$iss$iss)

df2 = melt.data.table(df, id.vars = "year", variable.name = "scenario", value.name = "ISS")
df2.haul = df2

>>>>

## Data
```{r}

@@

out_5.2 = readRDS(file = "C:/Users/bstacy2/OneDrive - UW/UW Postdoc/GitHub Repos/baseISS_data/outputs/paper_output/paper_scenario_5.2_ISS_500iters_output_2025-01-27.RDS")

out_9.2 = readRDS(file = "C:/Users/bstacy2/OneDrive - UW/UW Postdoc/GitHub Repos/baseISS_data/outputs/paper_output/paper_scenario_9.2_ISS_500iters_output_2025-01-27.RDS")

out_4.2 = readRDS(file = "C:/Users/bstacy2/OneDrive - UW/UW Postdoc/GitHub Repos/baseISS_data/outputs/paper_output/paper_scenario_4.2_ISS_500iters_output_2025-01-28.RDS")

out_2.2 = readRDS(file = "C:/Users/bstacy2/OneDrive - UW/UW Postdoc/GitHub Repos/baseISS_data/outputs/paper_output/paper_scenario_2.2_ISS_500iters_output_2025-01-28.RDS")

@@

## ISSB Results 
### * Time series 2 panel

@@

@@

### * 2003 and 2004 histograms
```{r, fig.height=8, fig.width=9}

@@

@@

@@

### * Time seris components

@@

```{r, fig.height=5.5}
sub_range = out_5.2$length$iss$YEAR %in% 1977:2023

par(mfrow = c(1,1))
plot(out_5.2$length$iss$YEAR[sub_range], out_5.2$length$iss$iss[sub_range], type = "l", ylab = "ISSB", cex.lab = 1.3, col = "black", ylim = c(0, 25000), xlab = "Year")
lines(out_9.2$length$iss$YEAR[sub_range], out_9.2$length$iss$iss[sub_range], type = "l", col = "blue") 
lines(out_4.2$length$iss$YEAR[sub_range], out_4.2$length$iss$iss[sub_range], type = "l", col = "orange") 
lines(out_2.2$length$iss$YEAR[sub_range], out_2.2$length$iss$iss[sub_range], type = "l", col = "green")
lines(out_1.4$length$iss$YEAR[sub_range], out_1.4$length$iss$iss[sub_range], type = "l", col = "red")

legend("topleft", legend = c("boot length", "boot length + haul", "boot all", "boot all + sampling strata weighting", "full"), lty = c(1,1,1,1,1), col = c("black", "blue", "orange", "green", "red"), bty = "n")
```

@@

## Optimize Sampling
### * Time series Expansion X Samples 10, 20, 30
```{r, fig.width=9, fig.height=5}
out_2.1.1 = readRDS(file = "C:/Users/bstacy2/OneDrive - UW/UW Postdoc/GitHub Repos/baseISS_data/outputs/paper_output/paper_scenario_2.1.2_ISS_500_iters_2025-01-28.RDS")

df = tidytable(year = year,
               N10_Enone = out_2.1.1$samples_10$expansion_NULL$length$iss$iss,
               N20_Enone = out_2.1.1$samples_20$expansion_NULL$length$iss$iss,
               N30_Enone = out_2.1.1$samples_30$expansion_NULL$length$iss$iss,
               N10_Emedium = out_2.1.1$samples_10$expansion_haul_numbers$length$iss$iss,
               N20_Emedium = out_2.1.1$samples_20$expansion_haul_numbers$length$iss$iss,
               N30_Emedium = out_2.1.1$samples_30$expansion_haul_numbers$length$iss$iss,
               N10_Efull = out_2.1.1$samples_10$expansion_haul_month_numbers$length$iss$iss,
               N20_Efull = out_2.1.1$samples_20$expansion_haul_month_numbers$length$iss$iss,
               N30_Efull = out_2.1.1$samples_30$expansion_haul_month_numbers$length$iss$iss,)
